---
title: "R_class"
output: html_document
date: "2023-05-07"
---

## import library

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## R Markdown

This data frame contains the following columns:

low: indicator of birth weight less than 2.5 kg.
age: mother's age in years.
lwt: mother's weight in pounds at last menstrual period.
race: mother's race (1 = white, 2 = black, 3 = other).
smoke:smoking status during pregnancy.
ptl:number of previous premature labours.
ht:history of hypertension.
ui:presence of uterine irritability.
ftv: number of physician visits during the first trimester.
bwt:birth weight in grams.
```{r cars}
library(MASS) # Load MASS for the birthwt data set
summary(birthwt)
head(birthwt)
## Including Plots
```

```{r}
library(MASS) # Load MASS for the birthwt data set

# Use smoke as the faceting variable
ggplot(birthwt, aes(x = bwt)) +
  geom_histogram() +
  facet_grid(smoke ~ .)
## Including Plots
```
You can also embed plots, for example:



```{python}
a = 1
print(a)
```



```{r}
# Convert smoke to a factor and reassign new names
birthwt_mod <- birthwt %>% 
    mutate(smoke=case_when(smoke == "1" ~ "Smoke", smoke == "0" ~ "No Smoke")) %>%
    mutate(race=case_when(race == "1"~ "white",race == "2"~ "black", race == "3"~ "other"))
           
summary(birthwt_mod)
head(birthwt_mod)

```

## Scatror plot
```{r }

ggplot(data=birthwt_mod, aes(x=lwt, y=bwt))+geom_point(aes(color=race))+  geom_smooth(method = lm)

ggplot(data=birthwt_mod, aes(x=lwt, y=bwt))+geom_point(aes(color=race))+  geom_smooth()

```

## histogram
```{r }

ggplot(birthwt_mod, aes(x = bwt, fill = smoke)) +
  geom_histogram(position = "identity", alpha = 0.4)

ggplot(birthwt_mod, aes(x = bwt, fill = race)) +
  geom_histogram(position = "identity", alpha = 0.6)
```

## boxplot
```{r }

ggplot(birthwt_mod, aes(y = bwt,  x= smoke, fill = smoke)) +
  geom_boxplot()

```
```{r }
library(ggstatsplot)
ggbetweenstats(
  data  = birthwt_mod,
  x     = smoke,
  y     = bwt,
  title = "Distribution of bwt"
)

```


## T-test
```{r }
t.test(bwt~smoke, data = birthwt_mod)

```
pvalue = 0.007 < 0.05 , so it is significant
